---
title: "Examples of UW Figures"
author: "Jen Birstler <birstler@wisc.edu>"
output: 
  html_document: 
    highlight: tango
    toc: yes
    toc_float: yes
    code_folding: hide
vignette: >
  %\VignetteIndexEntry{Aesthetic specifications}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  fig.dpi = 96,
  collapse = TRUE,
  comment = "#>",
  out.width = "98%"
)
```

```{r setup}
library(biostatrpts)
set.seed(123)
```

# uwAccrualBars

```{r fig.asp = 0.5, fig.width = 8}
NN <- 200
# generate random enrollment dates over
randoDates <- data.frame(date = paste0(sample(1:12, size = NN, replace = TRUE),
                                       "/01/",
                                       sample(2019:2020, size = NN, replace = TRUE)),
                         trt = sample(LETTERS[1:2], NN, replace = TRUE))

 uwAccrualBars(
   accData = randoDates, dateName = "date", trxName = NULL,
   interval = "month", yLim = NULL, pHoriz = FALSE, pBeside = FALSE,
   linedbars = FALSE
 )
```

# uwBar
Called internally

```{r fig.asp = 0.5, fig.width = 8}
mat <- matrix(1:12, nrow = 3)
dimnames(mat) <- list(c("A", "B", "C"), c("D", "E", "F", "G"))
uwBar(mat,
   pBeside = TRUE, pHoriz = FALSE, lined = FALSE,
   axLim = NULL, yLab = NULL, xLab = NULL, printBarVals = TRUE,
   Legend = TRUE, LegendLoc = "topleft", LegendCex = 0.8,
   mgp.y = c(3, 1, 0), mgp.x = c(3, 1, 0), cex.names = 1, barNamesLas = 1,
   barNamesSeq = 1, barNamesAngle = 0, digits = 1
)
```

# uwBarPlot {.tabset}

```{r}
TRT <- rep(c("A", "B", "C"), 30)
AE <- ordered(
  sample(c("None", "Mild", "Moderate", "Severe"), 90, replace = TRUE),
  c("None", "Mild", "Moderate", "Severe")
)
data <- data.frame(TRT, AE)
```

## Example 1

```{r fig.asp = 0.4, fig.width = 8}
uwBarPlot(
  demoData = data, trxName = NULL, factorName = "AE", Legend = TRUE, demoBarPlot = FALSE,
  pHoriz = TRUE, pBeside = TRUE, xLab = "Number of Subjects", pTitle = "Adverse Events",
  digits = 1, barNamesAngle = 60, cex.names = 0.8, lined = FALSE, Percent = FALSE,
  barNamesLas = 1, barNamesSeq = 1, printPVals = TRUE, pTest = "f", pValCex = 0.6,
  LatexFileName = NULL, LegendLoc = "topright"
)
```

## Example 2

```{r fig.asp = 0.6, fig.width = 8}
uwBarPlot(
  demoData = data, trxName = "TRT", factorName = "AE", Legend = TRUE, demoBarPlot = TRUE,
  pHoriz = TRUE, xLab = "Number of Subjects", pTitle = "Adverse Events", digits = 1,
  barNamesAngle = 0, lined = FALSE, Percent = FALSE, barNamesLas = 0, barNamesSeq = 1,
  printPVals = TRUE, pTest = "f", pValCex = 0.6, LatexFileName = NULL, LegendLoc = "topleft",
  pStrWrap = TRUE
)
```

## Example 3

```{r fig.asp = 0.6, fig.width = 8}
uwBarPlot(
  demoData = data, trxName = "TRT", factorName = "AE", Legend = TRUE, demoBarPlot = FALSE,
  pHoriz = FALSE, yLab = "Percent of Subjects", pTitle = "Adverse Events", digits = 1,
  barNamesAngle = 0, lined = FALSE, Percent = TRUE, barNamesLas = 1, barNamesSeq = 1,
  printPVals = TRUE, pTest = "f", pValCex = 0.6, LatexFileName = NULL, LegendLoc = "bottomleft"
)
```

# uwBox
Called internally

```{r fig.asp = 0.4, fig.width = 8}
TRT <- c(rep("A", 20), rep("B", 20), rep("C", 20))
metric <- c(rnorm(20, 2, 1), rnorm(20, 3, 1), rnorm(20, 4, 1))
dat <- data.frame(TRT, metric)
uwBox(dat, "TRT", "metric")
```


# uwBoxPlot

```{r fig.asp = .7, fig.width = 8}
TRT <- c(rep("A", 20), rep("B", 20), rep("C", 20))
metric <- c(rnorm(20, 2, 1), rnorm(20, 3, 1), rnorm(20, 4, 1))
dat <- data.frame(TRT, metric)
uwBoxPlot(
  data = dat,
  trxName = "TRT",
  metricName = "metric",
  LatexFileName = NULL,
  showTab = FALSE,
  pTitle = "Example of uwBoxPlot",
  yLab = "Weight of Something (oz)",
  plotMean = FALSE, pOutliers = FALSE,
  boxWex = 0.75,
  Ropen = FALSE,
  printPVals = TRUE,
  pTest = "t",
  abbrevN = 1,
  pairwise = TRUE,
  trxControl = NULL,
  pExclude = NULL,
  pInclude = list(
    list(c("A", "B"), "C"), list("B", "C"),
    list("A", "C")
  ),
  yLim = NULL,
  pStrWrap = FALSE,
  pValCex = 0.7,
  LatexCaption = NULL,
  col.just = c("|l|", rep("c", 10), "|r", "r|"),
  firstCol.name = NULL
)
```


# uwConfBands {.tabset}

```{r}
data(colon, package = "survival")
colon$sex.f <- factor(colon$sex, levels = c(0, 1), labels = c("Female", "Male"))
colon$surg.f <- factor(colon$surg,
  levels = c(0, 1),
  labels = c("Short", "Long")
)
colon$differ.f <- factor(colon$differ,
  levels = c(1, 2, 3),
  labels = c("Well", "Moderate", "Poor")
)
```

## Example 1

```{r fig.asp = 0.6, fig.width = 8}
uwConfBands(
  fullDat = colon,
  trxName = "rx",
  trxLevels = c("Obs", "Lev"),
  factVarNames = c("sex.f", "age", "surg.f", "differ.f"),
  factFigNames = c("Gender", "Age", "Time to Reg.", "Tumor Diff."),
  estimate = "m",
  metricName = "nodes",
  printPVals = FALSE,
  LatexFileName = NULL
)
```

## Example 2

```{r fig.asp = 0.6, fig.width = 8}
uwConfBands(
  fullDat = colon,
  trxName = "rx",
  trxLevels = c("Obs", "Lev"),
  factVarNames = c("sex.f", "age", "surg.f", "differ.f"),
  factFigNames = c("Gender", "Age", "Time to Reg.", "Tumor Diff."),
  estimate = "p",
  statusName = "status",
  printPVals = TRUE,
  LatexFileName = NULL
)
```

## Example 3

```{r fig.asp = 0.6, fig.width = 8}
uwConfBands(
  fullDat = colon,
  trxName = "rx",
  trxLevels = c("Obs", "Lev"),
  factVarNames = c("sex.f", "age", "surg.f", "differ.f"),
  factFigNames = c("Gender", "Age", "Time to Reg.", "Tumor Diff."),
  estimate = "h",
  statusName = "status",
  timeName = "time",
  xLim = c(0.25, 5),
  xLog = TRUE,
  printPVals = TRUE,
  interactPVals = TRUE,
  LatexFileName = NULL
)
```

## Example 4

```{r fig.asp = 0.6, fig.width = 8}
uwConfBands(
  fullDat = colon,
  trxName = "rx",
  trxLevels = c("Obs", "Lev"),
  factVarNames = c("sex.f", "age", "surg.f", "differ.f"),
  factFigNames = c("Gender", "Age", "Time to Reg.", "Tumor Diff."),
  estimate = "h",
  statusName = "status",
  timeName = "time",
  xLim = c(0, 2),
  xLog = FALSE,
  xDetailed = FALSE,
  printPVals = TRUE,
  interactPVals = TRUE,
  LatexFileName = NULL
)
```

# uwCumulAccr {.tabset}

```{r}
Dates <- c(
  "03/01/2008", "09/01/2007", "07/01/2007", "12/01/2006", "08/01/2007", "08/01/2007",
  "04/01/2007", "04/01/2007", "04/01/2007", "11/01/2006", "11/01/2006", "12/01/2006",
  "12/01/2006", "10/01/2006", "01/01/2007", "11/01/2006", "12/01/2006", "02/01/2007",
  "08/01/2007", "08/01/2006", "09/01/2006", "04/01/2007", "05/01/2007", "11/01/2006",
  "10/01/2006", "03/01/2007", "10/01/2007", "07/01/2007", "03/01/2007", "04/01/2006",
  "05/01/2006", "11/01/2006", "12/01/2006", "02/01/2007", "02/01/2007", "02/01/2007",
  "04/01/2007", "05/01/2007", "07/01/2007", "08/01/2007", "11/01/2007", "10/01/2007",
  "09/01/2007", "10/01/2007", "05/01/2007", "01/01/2008", "12/01/2006", "02/01/2007",
  "03/01/2007", "04/01/2007", "04/01/2007", "05/01/2007", "07/01/2007", "02/01/2007",
  "07/01/2007", "10/01/2007", "01/01/2008"
)
Date <- chron::chron(Dates, format = c(dates = "m/d/y"))
TRT <- rep(c("A", "B"), c(30, 27))
data <- data.frame(Date, TRT)
```

## Example 1

```{r fig.asp = 0.6, fig.width = 8}
uwCumulAccr(
  accData = data, dateName = "Date", trxName = NULL,
  yLab = "Cumulative Number of Subjects",
  yLim = NULL,
  pTitle = "Accural over Time for Total Cohort",
  projectLine = list(PatsPerTRT = as.numeric(), DaysPerTRT = as.numeric())
)
```

## Example 2

```{r fig.asp = 0.6, fig.width = 8}
# Projected accrual of 32 per arm over 750 days
uwCumulAccr(
  accData = data, dateName = "Date", trxName = NULL,
  yLab = "Cumulative Number of Subjects",
  yLim = NULL, startDate = "01/01/2006",
  pTitle = "Total Cohort with equal projected accrual",
  projectLine = list(PatsPerTRT = 64, DaysPerTRT = 750)
)
```

## Example 3

```{r fig.asp = 0.6, fig.width = 8}
uwCumulAccr(
  accData = data, dateName = "Date", trxName = "TRT",
  yLab = "Cumulative Number of Subjects",
  yLim = NULL,
  pTitle = "Accural over Time by Treatment Arm",
  projectLine = list(PatsPerTRT = as.numeric(), DaysPerTRT = as.numeric())
)
```

## Example 4

```{r fig.asp = 0.6, fig.width = 8}
# Projected accrual of 30 in A and 27 in B over 700 days
uwCumulAccr(
  accData = data, dateName = "Date", trxName = "TRT",
  yLab = "Cumulative Number of Subjects",
  yLim = c(0, 70), LegendCor = c(25, 55),
  pTitle = "Accural over Time by Treatment Arm",
  projectLine = list(PatsPerTRT = c(30, 27), DaysPerTRT = 700)
)
```

# uwLeveledBoxPlot {.tabset}

```{r}
trt1 <- rep(rep(c("A", "B", "C"), 120), 3)
fctr1 <- as.factor(rep(c(rep("Female", 180), rep("Male", 180)), 3))
mtrc1 <- rnorm(360 * 3, 10, 4)
upfct <- c(rep("Baseline", 360), rep("Week 12", 360), rep("Week 24", 360))
ids <- as.character(c(1:360, 1:360, 1:360))
dat1 <- data.frame(trt1, fctr1, mtrc1, upfct, ids)
```

## Example 1

```{r fig.asp = 0.6, fig.width = 8}
uwLeveledBoxPlot(
  allData = dat1,
  trxName = "trt1",
  metricName = "mtrc1",
  lowfactName = "fctr1",
  hifactName = "upfct",
  delta = FALSE,
  baseLevel = "Baseline",
  idName = "ids",
  LatexFileName = NULL,
  showTab = FALSE,
  Legend = FALSE,
  pTitle = "Example of uwLeveledBoxPlot",
  yLab = "Random Normal",
  plotMean = TRUE, pOutliers = FALSE,
  lWhisker = .05, hWhisker = .95,
  lHinge = .25, hHinge = .75,
  boxWex = 0.75,
  printPVals = TRUE,
  PVinTableOnly = FALSE,
  PValCex = 0.5,
  Ropen = FALSE,
  pTest = "t",
  abbrevN = 1,
  pairwise = TRUE,
  trxControl = NULL,
  pExclude = NULL,
  yLim = NULL
)
```

## Example 2

```{r fig.asp = 0.6, fig.width = 8}
uwLeveledBoxPlot(
  allData = dat1,
  trxName = "trt1",
  metricName = "mtrc1",
  lowfactName = "fctr1",
  hifactName = "upfct",
  delta = TRUE,
  deltaPct = FALSE,
  baseLevel = "Baseline",
  idName = "ids",
  LatexFileName = NULL,
  showTab = FALSE,
  Legend = TRUE,
  LegendLoc = "topleft",
  pTitle = "Example of uwLeveledBoxPlot with delta=TRUE",
  yLab = "Random Normal",
  plotMean = FALSE, pOutliers = FALSE,
  lWhisker = .05, hWhisker = .95,
  lHinge = .25, hHinge = .75,
  boxWex = 0.75,
  printPVals = TRUE,
  PVinTableOnly = FALSE,
  PValCex = 0.5,
  Ropen = FALSE,
  pTest = "w",
  abbrevN = 1,
  pairwise = TRUE,
  trxControl = NULL,
  pExclude = NULL,
  pInclude = list(list(c("A", "B"), "C"), list("A", c("B", "C")), list("A", "C")),
  yLim = NULL
)
```

## Example 3

```{r fig.asp = 0.6, fig.width = 8}
uwLeveledBoxPlot(
  allData = dat1,
  trxName = "trt1",
  metricName = "mtrc1",
  lowfactName = "fctr1",
  hifactName = "upfct",
  delta = TRUE,
  deltaPct = TRUE,
  baseLevel = "Baseline",
  idName = "ids",
  LatexFileName = NULL,
  showTab = FALSE,
  Legend = TRUE,
  LegendLoc = "topleft",
  pTitle = "Example of uwLeveledBoxPlot with deltaPct=TRUE",
  yLab = "Random Normal",
  plotMean = FALSE, pOutliers = FALSE,
  lWhisker = .05, hWhisker = .95,
  lHinge = .25, hHinge = .75,
  boxWex = 0.75,
  printPVals = TRUE,
  PVinTableOnly = FALSE,
  PValCex = 0.5,
  Ropen = FALSE,
  pTest = "w",
  abbrevN = 1,
  pairwise = TRUE,
  trxControl = NULL,
  pExclude = NULL,
  pInclude = list(list(c("A", "B"), "C"), list("A", c("B", "C")), list("A", "C")),
  yLim = NULL
)
```

# uwLineGraph

```{r fig.asp = 0.6, fig.width = 8}
TRT <- rep(rep(c("A", "B", "C"), c(20, 20, 20)), 4)

ptID <- rep(1:60, 4)
ptID <- factor(ptID)

numVar <- c(
  rnorm(20, 0, 1), rnorm(20, 1, 1), rnorm(20, 2, 1), rnorm(20, 3, 1),
  rnorm(20, 3, 1), rnorm(20, 10, 1), rnorm(20, 2, 3), rnorm(20, 0, 1),
  rnorm(20, 6, 1), rnorm(20, 1, 3), rnorm(20, 2, 5), rnorm(20, 3, 1)
)

timeVar <- rep(c("Baseline", "3 Months", "6 Months", "12 Months"), c(60, 60, 60, 60))
timeVar <- ordered(
  timeVar,
  c("Baseline", "3 Months", "6 Months", "12 Months")
)

df <- data.frame(TRT, ptID, numVar, timeVar)

uwLineGraph(
  data = df,
  metricName = "numVar",
  trxName = "TRT",
  factorName = "timeVar",
  LatexFileName = NULL,
  plotMean = TRUE,
  pch = NULL,
  colScale = TRUE,
  yLim = NULL,
  yLab = "",
  xLab = "",
  pTitle = "Example of uwLineGraph",
  refLines = TRUE,
  Legend = TRUE,
  LegendLoc = "topright",
  printPVals = TRUE,
  pTest = "t",
  pExclude = NULL,
  trxControl = "A",
  pairDiffTab = TRUE,
  ptIDname = "ptID",
  BaseLevel = "Baseline",
  numDec = 2,
  rowLines = list(c(FALSE), c(FALSE)),
  caption = list(c(NULL), c(NULL)),
  firstCol.name = "Time",
  Ropen = FALSE
)
```

# uwPairedBoxPlot

```{r fig.asp = 0.6, fig.width = 8}
Time <- ordered(c(rep("Pre", 100), rep("Post", 100)), c("Pre", "Post"))
ID <- rep(sample(c(1:100), 100, replace = FALSE), 2) # IDs will not be in order
weight <- c(rnorm(100, 200, 3), rnorm(100, 197, 3)) # pretend they are paired

ID[3] <- NA
ID[176] <- NA # Possible missing data
ID[150] <- 101 # Say someone as only one reading in post

dat <- data.frame(Time, ID, weight)

uwPairedBoxPlot(
  allData = dat,
  pairName = "Time",
  metricName = "weight",
  ptID = "ID",
  onlyPairs = TRUE,
  plotDiff = TRUE,
  chgLayout = TRUE,
  pWilcox = TRUE,
  LatexFileName = NULL,
  pTitle = "uwPairedBoxPlot Example",
  yLab = "Weight (lbs.)",
  plotMean = FALSE, pOutliers = FALSE,
  lWhisker = .05, hWhisker = .95,
  lHinge = .25, hHinge = .75,
  boxWex = .75,
  printPVals = TRUE,
  yLim = NULL,
  footNote = NULL,
  firstCol.name = NULL,
  LatexCaption = NULL,
  caption.loc = "bottom",
  showTab = FALSE,
  label = NULL
)
```

# uwPairedLeveledBoxPlot

```{r fig.asp = 1, fig.width = 8}
trt <- rep(c("Case", "Control"), 60)
id <- rep(rep(1:20, rep(2, 20)), 3)
fact <- rep(c("A", "B", "C"), c(40, 40, 40))
met <- c(rnorm(40, 10), rnorm(40, 11), rnorm(40, 12))

df <- data.frame(trt, id, fact, met)
uwPairedLeveledBoxPlot(
  pairData = df, pairName = "trt", metricName = "met",
  factorName = "fact", ptID = "id",
  LatexFileName = NULL,
  yLab = "Normal", pTest = "w",
  pTitle = "Example of uwPairedLeveledBoxPlot",
  plotMean = TRUE, pOutliers = FALSE,
  lWhisker = .05, hWhisker = .95,
  rowLines = c(FALSE, TRUE, FALSE, TRUE, FALSE, TRUE),
  lHinge = .25, hHinge = .75,
  boxWex = 0.75, printPVals = TRUE
)
```

# uwSimpleReg

```{r fig.asp = 0.6, fig.width = 8}
Xvar <- rnorm(50, -10, 1)
Yvar <- 0.5 * Xvar + rnorm(50, 0, 1)

dfLin <- data.frame(Xvar, Yvar)

layout(1)
uwSimpleReg(
  Data = dfLin, respVar = "Yvar", depVar = "Xvar",
  main = "Example of uwSimpleReg",
  ylab = "Example Response", xlab = "Example Explanatory",
  ylim = NULL, xlim = NULL, printPVal = TRUE, printModel = TRUE, printRsq = TRUE
)
```

# uwSurvival

```{r fig.asp = 0.8, fig.width = 8}
death <- sample(c(0, 1), 200, replace = TRUE, prob = c(0.4, 0.6))
trt <- rep(c("ABDC", "ABGH"), c(100, 100))
time <- ceiling(runif(200, 0, 100))

sData <- data.frame(death, trt, time)
uwSurvival(
  survData = sData, statusName = "death", trxName = "trt", trxControl = "ABDC",
  timeName = "time", pTitle = "Survival by Treatment",
  yLab = "Percent of Survival Probability",
  xLab = "Days from Randomization", pValCex = 0.8, SScex = 0.7,
  markCensor = FALSE, Legend = TRUE, LegendLoc = "topright",
  LatexFileName = c(
    paste(getwd(), "surv1.tex", sep = ""),
    paste(getwd(), "/surv2.tex", sep = "")
  ),
  showTab = FALSE, printPVals = TRUE, printSS = TRUE,
  Ropen = FALSE, GraphSSfreq = 5, TableSSfreq = 1, firstCol.name = NULL,
  LatexCaption = NULL, SSinPlot = TRUE,
  size = "scriptsize"
)
```




